# Off-target analysis

Similar to the on-target analysis, the off-target analysis contains the same types of tables and figures. Table 4 indicates the read counts in **bold** for each specimen and off-target site. Proportions below in plain text indicate the uncharacterized, complete, insertion containing, or deletion containing sequences.

```{r off_tar_summary_tbl}
off_tar_summary_print <- off_tar_summary_tbl %>%
  dplyr::group_by(specimen, rname) %>%
  dplyr::mutate(
    "Reads" = pNums(total.cnt, digits = 0),
    "Unchar." = pNums(unc.freq),
    "Complete" = pNums(com.freq),
    "Insertion" = pNums(in.freq),
    "Deletion" = pNums(del.freq)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::select(
    specimen, rname, Reads, Unchar., Complete, Insertion, Deletion
  ) %>%
  tidyr::gather(Type, val, -specimen, -rname) %>%
  tidyr::spread(rname, val, fill = "-") %>%
  dplyr::mutate(
    specimen = factor(
      specimen, 
      levels = unique(str_extract(sample_info$sampleName, "[\\w]+"))),
    Type = factor(
      Type , 
      levels = c("Reads", "Unchar.", "Complete", "Insertion", "Deletion")
    )
  ) %>%
  dplyr::arrange(specimen, Type) %>%
  dplyr::rename("Specimen" = specimen)

if( args$tables ){
  
  off_tar_summary_print %>%
    write.csv(
      file = file.path(tables_path, "tbl4.off_target_editing.csv"),
      quote = TRUE, row.names = FALSE
    )
  
}

kable(
    x = off_tar_summary_print[,-1], format = report_format, row.names = FALSE,
    booktabs = TRUE, longtable = TRUE, escape = FALSE, caption = tbl_caps[4],
    format.args = list(big.mark = ",")
  ) %>%
  kableExtra::kable_styling(
    bootstrap_options = bootstrap_options,
    latex_options = latex_options
  ) %>%
  kableExtra::group_rows(
    index = table(paste0("Specimen: ", off_tar_summary_print$Specimen))
  ) %>%
  kableExtra::row_spec(grep("Reads", off_tar_summary_print$Type), bold = TRUE)

```

In a similar fashion to Figures 1 and 2, Figures 3 and 4 display the frequency of different types of reads across samples and off-target sites and the distribution of deleted sequences at the off target sites.

```{r off_tar_graphic, fig.width=7.5, fig.height=3.5}
off_tar_plot_data <- off_tar_summary_tbl %>%
  dplyr::select(-total.cnt) %>%
  tidyr::gather(key = type, value = freq, -specimen, -rname) %>%
  dplyr::mutate(
    rname = factor(
      rname, levels = panel_targets$target[panel_targets$edit == "off"]
    ),
    specimen = factor(
      specimen, levels = unique(str_extract(sample_info$sampleName, "[\\w]+"))
    ),
    type = factor(
      type, levels = c("unc.freq", "com.freq", "in.freq", "del.freq")
    )
  ) %>%
  dplyr::arrange(desc(type))

levels(off_tar_plot_data$type) <- c(
  "Unchar.", "Complete", "Insertion", "Deletion"
)

off_tar_graphic <- ggplot(
    off_tar_plot_data, aes(x = rname, y = freq, group = specimen)
  ) + 
  geom_bar(stat = "identity", aes(fill = type)) + 
  facet_wrap(~ specimen, nrow = 1) +
  scale_fill_brewer(type = "qual", palette = "Paired") +
  labs(x = NULL, y = "Frequency", fill = NULL) +
  custom_theme +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

ggsave(
  filename = "off_target_editing.pdf", 
  plot = off_tar_graphic, 
  device = "pdf", 
  path = figure_path, 
  width = figure_width, 
  height = 3.5, 
  units = "in"
)

ggsave(
  filename = "off_target_editing.png", 
  plot = off_tar_graphic, 
  device = "png", 
  path = figure_path, 
  width = figure_width,
  height = 3.5, 
  units = "in",
  dpi = knitr::opts_chunk$get("dpi")
)


if( args$format == "pdf"){
  
  knitr::include_graphics(
    path = file.path(figure_path, "off_target_editing.pdf")
  )
  
}else{
  
  knitr::include_graphics(
    path = file.path(figure_path, "off_target_editing.png")
  )
  
}
```

```{r} 
cat(fig_caps[3]) 
```

```{r off_tar_del_profile, fig.width=7.5, fig.height=2.15}
off_del_profile <- edit_grl$D[edit_grl$D$edit == "off"]

off_del_profile <- off_del_profile[
  rep(seq_along(off_del_profile), off_del_profile$count)
]

off_del_profile$count <- NULL

off_del_profile <- split(off_del_profile, off_del_profile$specimen)

null <- lapply(seq_along(off_del_profile), function(i, target, totals, fp){
  
    p <- plot_indel_cov(off_del_profile[[i]], target, totals = totals) + 
      custom_theme
    
    file_pdf <- sprintf("off_target_del_profile-%s.pdf", i)
    file_png <- sprintf("off_target_del_profile-%s.png", i)
      
    ggsave(
      filename = file_pdf, 
      plot = p, 
      device = "pdf", 
      path = fp, 
      width = figure_width, 
      height = 2.15, 
      units = "in"
    )
    
    ggsave(
      filename = file_png, 
      plot = p, 
      device = "png", 
      path = fp, 
      width = figure_width,
      height = 2.15, 
      units = "in",
      dpi = knitr::opts_chunk$get("dpi")
    )
    
  },
  target = norm_targets,
  totals = total_specimen_counts,
  fp = figure_path
)

if( args$format == "pdf"){
  
  knitr::include_graphics(
    path = sprintf(
      file.path(figure_path, "off_target_del_profile-%s.pdf"), 
      seq_along(off_del_profile)
    )
  )
  
  
}else{
  
  knitr::include_graphics(
    path = sprintf(
      file.path(figure_path, "off_target_del_profile-%s.png"), 
      seq_along(off_del_profile)
    )
  )
  
}

```

```{r} 
cat(fig_caps[4]) 
```